---
output: pdf_document
---

```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\doublespacing

# Appendix B: R Code for Chapter 6 {-}

\singlespace

Required: R Packages from CRAN

\small
```{r, echo=TRUE, eval=FALSE}
if (!require(tidyverse)){
  install.packages("tidyverse")
  library(tidyverse)
}
if (!require(furniture)){
  install.packages("furniture")
  library(furniture)
}
if (!require(here)){
  install.packages("here")
  library(here)
}
if (!require(devtools)){
  install.packages("devtools")
  library(devtools)
}
if (!require(survey)){
  install.packages("survey")
  library(survey)
}
```
\normalsize

Required: R Packages from GitHub

\small
```{r, echo=TRUE, eval=FALSE}
if (!require(MarginalMediation)){
  devtools::install_github("tysonstanley/MarginalMediation")
  library(MarginalMediation)
}
```
\normalsize

\clearpage

## Data Preparation {-}

Data preparation using the 2014 National Survey on Drug Use and Health, as described in Chapter 4.

\small
```{r app_data, eval=FALSE}
```
\normalsize

\clearpage

## Models {-}

\small
```{r app_models, eval=FALSE}
```
```{r app_data2, eval=FALSE}
```
```{r app_odds, eval=FALSE}
```
\normalsize

\clearpage

## Tables and Figures {-}

Table \ref{tab:table1} on page \pageref{tab:table1}

\small
```{r app_table1, eval=FALSE}
```
\normalsize

Table \ref{tab:perc} on page \pageref{tab:perc}

\small
```{r app_tab_perc, eval=FALSE}
```
\normalsize

Table \ref{tab:oldperc} on page \pageref{tab:oldperc}

\small
```{r old_perc, eval=FALSE}
```
\normalsize

Figure \ref{fig:app} on page \pageref{fig:app}

\small
```{r app_fig, eval=FALSE}
```

\normalsize