---
title: "Towards a Framework for Operational Risk in the Banking Sector"
author: "Mphekeleli Hoohlo"
csl: ref_format.csl
output:
  pdf_document:
    includes:
      in_header: preamble.tex
    keep_tex: yes
    latex_engine: xelatex
  word_document: default
geometry:
- top=1in
- bottom=1in
- right=1in
- left=1.5in
nocite: |
  @Burnham2002
  @Iacobucci2007
  @Mood2010
  @Norton2012
  @Edwards2007
  @Hastie2009
documentclass: DissertateUSU
params:
  chair: Eric Schaling, Ph.D.
  committee1: Thanti Mthanti, Ph.D.
  committee2: Odongo Kodongo, Ph.D.
  committee3: Thabang Mokoaleli-Mokoteli, Ph.D.
  committee4: Christopher Malikane, Ph.D.
  degree: Doctor of Philosophy
  field: Risk Theory (Finance)
  gradschool: Paul Alagidede, Ph.D.
  year: '2019'
bibliography: Diss.bib
---


```{r global_options, include=FALSE}
## This saves you from having to do this for every chunk
knitr::opts_chunk$set(fig.path = 'figures/',
                      echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)
## Do NOT Remove
dissertateUSU::preamble_for_title()
```

<!-- Title page printed automatically -->
\pagenumbering{roman}
\pagestyle{empty}
\copyrightpage

<!-- Abstract -->
\newpage
\pagestyle{fancy}
\fancyhead[L]{Abstract}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\chapter*{ABSTRACT}
\addcontentsline{toc}{section}{Abstract}
```{r child = 'abstract.Rmd'}
```

<!-- Public Abstract -->
\newpage
\fancyhead[L]{Public Abstract}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\chapter*{PUBLIC ABSTRACT}
\addcontentsline{toc}{section}{Public Abstract}
```{r child = 'abstract_public.Rmd'}
```

<!-- Dedication -->
\newpage
\fancyhead[L]{Dedication}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\chapter*{DEDICATION}
\addcontentsline{toc}{section}{Dedication}
```{r child = 'dedication.Rmd'}
```

<!-- Acknowledgements -->
\newpage
\fancyhead[L]{Acknowledgments}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{section}{Acknowledgments}
```{r child = 'acknowledgements.Rmd'}
```

<!-- Front Matter -->
\newpage
\fancyhead[L]{Table of Contents}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\tableofcontents

\newpage
\fancyhead[L]{List of Tables}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\listoftables

\newpage
\fancyhead[L]{List of Figures}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\listoffigures


\newpage
\pagenumbering{arabic}

<!-- Introduction -->
\newpage
\fancyhead[L]{Introduction}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{INTRODUCTION}
```{r child = 'chapter1.Rmd'}
```

\FloatBarrier

<!-- Chapter 2 -->
\newpage
\fancyhead[L]{Literature Review}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{LITERATURE REVIEW}
```{r child = 'chapter2.Rmd'}
```

\FloatBarrier

<!-- Chapter 3 -->
\newpage
\fancyhead[L]{Exposure-based Operational Risk Analysis}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{EXPOSURE-BASED OPERATIONAL RISK ANALYSIS}
```{r child = 'chapter3.Rmd'}
```


\FloatBarrier
\newpage
\fancyhead[L]{Methods for modeling OpRisk depending on covariates}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{METHODS FOR MODELING OPRISK DEPENDING ON COVARIATES}
```{r child = 'chapter4.Rmd'}
```


\FloatBarrier
\newpage
\fancyhead[L]{Theoretical investigations for the quantification of modern ORMF's}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{THEORETICAL INVESTIGATIONS INTO THE QUANTIFICATION OF MODERN ORMF'S}
```{r child = 'chapter5.Rmd'}
```

\FloatBarrier

\newpage
\fancyhead[L]{Results}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{RESULTS}
```{r child = 'chapter6.Rmd'}
```

\FloatBarrier

\newpage
\fancyhead[L]{Discussion}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter{DISCUSSION}
```{r child = 'chapter7.Rmd'}
```

\FloatBarrier

\newpage
\fancyhead[L]{References}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\chapter*{REFERENCES}

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.4in}
\setlength{\parskip}{6pt}
\noindent

<div id="refs"></div>

\clearpage
\addcontentsline{toc}{chapter}{APPENDICES}
\fancyhead[L]{Appendices}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\vspace*{\fill}
  \begin{center}
    APPENDICES 
  \end{center}
\vspace*{\fill}

\clearpage
```{r, child = "chapter5_appendix.Rmd", size="tiny"}
```
\clearpage
```{r, child = "chapter6_appendix.Rmd", size="tiny"}
```

\clearpage
\addcontentsline{toc}{chapter}{CURRICULUM VITA}
\fancyhead[L]{Vita}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}

\vspace*{\fill}
  \begin{center}
    CURRICULUM VITA
  \end{center}
\vspace*{\fill}

\clearpage

```{r child = 'cv_2018_01_01.Rmd'}
```






